Analysis of observational data, to calculate the Delayed-Tau model parameters

### 2025-02-05 thesis.qmd
comp-Tr

### Dwarf Galaxies

@@

[^6]: $R^2$ Measures the proportion of variance explained by the linear model. For a model to be acceptable the $R^2$ should be atleast $80\%$

@@

To begin with the morphological types of the galaxies we first need to understand possible incompatibilities of the given types of each catalog.

::: {#fig-TTypes layout-ncol="2"}
![Before the clipping of the transient types](compare/quickplots/Hubble%20Morphology.png)

@@

Scatter plots and the residuals of the Hubble Numerical morphological types show a good correlation between the two datasets, if we ignore the transient galaxies.
:::

>>>>

### Dwarf Galaxies {#sec-dwarves}

@@

[^6]: $R^2$ Measures the proportion of variance explained by the linear model. For a model to be acceptable the $R^2$ should be higher than $80\%$, or close to it if $\overline{\text{Residuals}}\approx 0$

@@

To begin with the morphological types of the galaxies, we first need to address possible potential inconsistencies in the classifications of the two catalogs. As we can see in @fig-TType-all, some galaxies "jump" from one side of the classification to the other side, depending on the catalog. These galaxies are dwarf galaxies, so we can safely assume that they are Tr type galaxies, as discussed in @sec-dwarves. For the rest of the analysis we will adopt the Numerical Morphological Type from the HECATE catalog, since it includes a larger number of galaxies, ensuring better
data compatibility. Additionally, the HECATE catalog boasts an accuracy of 0.1 and provides errors in comparison with the UNGC.

::: {#fig-TTypes layout-ncol="2"}
![Before the clipping of the transient types](compare/quickplots/Hubble%20Morphology.png){#fig-TType-all}

@@

Scatter plots and the residuals of the Hubble Numerical morphological types show a good correlation between the two datasets, if we ignore the Transient dwarf galaxies.
:::
